Predicting Tags for StackOverflow Posts

### 2013-03-17 stackExchange/writeups/iccm-2013/writeup.tex
foo
Former-commit-id: 73f78ef349a2604d285356d5b4a9b81143a2a14f [formerly 6cbdf23c60e57f511e041763dc2489918180d760]
Former-commit-id: baceafc71a4ff08ba0dac57922c15bae12b0d47d

Note how model performance is almost identical for the calibration and test dataset (compare full model calibration to full model test).
This indicates that the model parameters were not overfit, and generalize well to the rest of the dataset.
It also provides evidence that \num{1000} posts is an adequate number to estimate model parameters accurately.

>>>>

Note how model performance is almost identical for the calibration and test dataset (compare full model calibration to full model test), which indicates that model parameters generalize well.
There is a small decrease in performance for test compared to calibration to the left of the vertical dotted line, and model performance at the dotted line is slightly lower (65\% compared to 67\%).
Model performance for the test dataset (cross-validated performance) is the most accurate measurement of real-world performance,
and model accuracy is 65\% for this dataset when tasked to predict one tag per post on average.
